Location of Shrimp Farms

### 2021-04-01 marine/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
finished a little datachecking for the methods

## write out bivalve taxa and production for Juliette
fao_bivalve_taxa_prod <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

>>>>

## write out bivalve taxa and production for Juliette
fao_bivalve_taxa_prod <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  # group_by(country, year) %>%
  # summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

sum(fao_bivalve_taxa_prod$fao_tonnes_production) # 17435623
unique(fao_bivalve_taxa_prod$country) # 42 countries

## When doing the filter for >500 tonnes by taxa group: 
# sum(fao_bivalve_taxa_prod$value) # 17446096
# unique(fao_bivalve_taxa_prod$country) # 43 countries - senegal added

### 2021-04-01 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished a little datachecking for the methods

We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm. However, aquaculture websites say there are 20 abalone farms, 14 oyster farms, and 25 mussel farms in Australia

@@

 - Abalone
  - https://www.oceanwatch.org.au/seafood/aquaculture/species/abalone/
  - “There are around 20 farms that produce about 725 tonnes of abalone every year, with production volume increasing by about 25% every year.”
  - 725 tonnes of abalone matches really well to what is reported for abalone in Australia by the FAO.

 - Oysters
  - This states that nearly all oyster license holders are a part of this association:   
  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
  - We will use this as truth: http://www.oysterssa.com.au/south-australian-oyster-growers
  - We will need to place an additional 14 oyster farms in Australia

 - Mussels
  - https://www.oceanwatch.org.au/seafood/aquaculture/species/mussels/
  - “Concentrated in the south of country, there are about 25 mussel farms spread across SA, Tasmania, Victoria, Tasmania and the south coasts of both NSW and WA.”

@@

# Jersey
Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are only 7 leases in Jersey.

>>>>

We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm. However, aquaculture websites say there are 20 abalone farms, 22 oyster farms, and 25 mussel farms in Australia

@@

 - Abalone
  - https://www.oceanwatch.org.au/aquaculture-species/
  - “There are around 20 farms that produce about 725 tonnes of abalone every year, with production volume increasing by about 25% every year.”
  - 725 tonnes of abalone matches really well to what is reported for abalone in Australia by the FAO.

 - Oysters
  - This states that nearly all oyster license holders are a part of this association:   
  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
  - We will use this as truth: https://oysterssa.com.au/oyster-growers/
  - We will need to place an additional 22 oyster farms in Australia

 - Mussels
  - https://www.oceanwatch.org.au/aquaculture-species/
  - “Concentrated in the south of country, there are about 25 mussel farms spread across SA, Tasmania, Victoria, Tasmania and the south coasts of both NSW and WA.”

@@

# Jersey
Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are 5 leases in Jersey.

### 2021-04-01 marine/marine_fish_general/finfish_farms/STEP1_fao_finfish_production.Rmd
finished a little datachecking for the methods

@@

>>>>

sum(explore$fao_tonnes_production) # 3901214
unique(explore$country) # 37 countries

## explore ASC and emod data

@@

```{r}
## write out bivalve taxa and production for Juliette
fao_finfish_taxa_prod <- fao %>%
  filter(species %in% finfish_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_finfish_taxa_prod$value) # 3916717

unique(fao_finfish_taxa_prod$country) # 37 countries 
```

### 2021-04-01 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
finished a little datachecking for the methods

sum(explore$fao_tonnes_production)

@@

>>>>

sum(explore$fao_tonnes_production) # 5094133
unique(explore$country) # 35 countries

## explore ASC data

@@

```{r}
## write out bivalve taxa and production for Juliette
fao_shrimp_taxa_prod <- fao %>%
  filter(species %in% shrimp_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_shrimp_taxa_prod$value) # 5095394 - adds ~1000 tonnes

unique(fao_shrimp_taxa_prod$country) # 35 countries 
```

### 2021-04-01 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished a little datachecking for the methods

write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))

@@

From FAO:
For marine aquaculture, the six shrimp breeding companies created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon. 2005b). These 4 325 full-time jobs were distributed as follows: 90 mariners, 1 072 in the processing plant, 400 in administration, 267 in hatcheries, 2 114 in farms, and 382 in other areas. This kind of shrimp farming also created 30 000 indirect jobs. Seaweed culture was being practised by 126 farmers.

@@

>>>>

75+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))

@@

From FAO: http://www.fao.org/fishery/countrysector/naso_madagascar/en

"For marine aquaculture, the **six shrimp breeding companies** created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon. 2005b). These 4 325 full-time jobs were distributed as follows: 90 mariners, 1 072 in the processing plant, 400 in administration, 267 in hatcheries, 2 114 in farms, and 382 in other areas. This kind of shrimp farming also created 30 000 indirect jobs. Seaweed culture was being practised by 126 farmers."

@@

 - Because this source doesn't have specifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.
